---
title: "Promethee Paper"
author: "Gabriel Felipe"
date: "February 21, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(reshape2)
library(plyr)
library(SparseM)
library(quantreg)
```

```{r read_noop_data}
options(warn = -1)
experiment_data0 <- read.csv("experiment0.csv", header = T, sep = ",")
experiment_data1 <- read.csv("experiment1.csv", header = T, sep = ",")
experiment_data2 <- read.csv("experiment2.csv", header = T, sep = ",")
```

# Infrastructure and Environment

We configured an experimental environment based on a Linux workstation which runs our Vanilla, Optimized and Umbu solution.

* Mem: 8GB RAM 1600 Mhz
* CPU: 8vCPUs - Intel(R) Core(TM) i7-4770S @ 3.10GHz CPU
* Kernel: 4.15.0-43-generic
* OS: 16.04.5-Ubuntu
* Hard disk: 1TB SEAGATE 7200 RPM
* Umbu Chunk Size: \(10^{7}\)

# Experiments

## How these solutions behave as the number of alternatives grows?

### Performance Metric

The performance metric is the duration to run each solution. This duration is given by the elapsed time between the start of the program until the time it is finished.

### Metodology

We executed the multi-criteria analysis on synthetic samples, made of randomly generated values, of 4096, 16385 and 65536 alternatives (in all these cases, we analysed a single criterion).

### Results

```{r vanilla_extrapolation}

vanilla_function = function(x){
  x * x
}

m <- ggplot(experiment_data0[experiment_data0$VERSION == 'vanilla',], aes(SIZE * SIZE, TIME)) + geom_point() + labs(x = "Input Size (Alternatives)",  y = "Time (Seconds)", title = "Vanilla Extrapolation")  + theme_bw()
m + xlim(0,150000) + stat_smooth(method="lm",fullrange=TRUE, formula = y ~ vanilla_function(x), colour = 'red')
```

```{r opt_extrapolation}

opt_function = function(x){
  x * (log(x)/log(2))
}

m <- ggplot(experiment_data0[experiment_data0$VERSION == 'opt',], aes(SIZE * SIZE, TIME)) + geom_point() + labs(x = "Input Size (Alternatives)",  y = "Time (Seconds)", title = "Optmized Extrapolation")  + theme_bw()
m + xlim(0,150000) + stat_smooth(method="lm",fullrange=TRUE, formula = y ~ opt_function(x), colour = 'green')
```

```{r umbu_extrapolation}

umbu_function = function(x){
  x * (log(x)/log(2))
}

m <- ggplot(experiment_data0[experiment_data0$VERSION == 'umbu',], aes(SIZE * SIZE, TIME)) + geom_point() + labs(x = "Input Size (Alternatives)",  y = "Time (Seconds)", title = "Umbu Extrapolation")  + theme_bw()
m + xlim(0,150000) + stat_smooth(method="lm",fullrange=TRUE, formula = y ~ umbu_function(x), colour = 'blue')
```

## How these solutions behave with a distinct frequency of repeated alternative?

### Performance Metric

The performance metric is the duration to run each solution. This duration is given by the elapsed time between the start of the program until the time it is finished.

### Metodology

We executed the multi-criteria analysis on specifics criteria of Seridó region based on his repetition rate. We selected the criteria with larger and smaller repetition rate, in addition to a criterion with typical rate [ in all these cases, we analysed a single criterion ].


### Results

``` {r summarize_function}
summarize <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = sd(x[[col]], na.rm=TRUE))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- rename(data_sum, c("mean" = varname))
 return(data_sum)
}

experiment_data1 <- summarize(experiment_data1, varname = "TIME", groupnames = c("VERSION", "SIZE"))
```

``` {r frequency_plot_vanilla}

p<- ggplot(experiment_data1[experiment_data1$VERSION == 'vanilla',], aes(SIZE,TIME, fill = VERSION)) + 
  geom_bar(stat="identity", color="black", position=position_dodge()) + 
  labs(x = "Version",y = "Time (Seconds)", title = "Vanilla Performance", fill = "Frequencies")  + theme_bw()
p

```

``` {r frequency_plot_vanilla2}

p<- ggplot(experiment_data1[experiment_data1$VERSION == 'vanilla',], aes(VERSION,TIME, fill = SIZE)) + 
  geom_bar(stat="identity", color="black", position=position_dodge()) + 
  labs(x = "Version",y = "Time (Seconds)", title = "Vanilla Performance", fill = "Frequencies")  + theme_bw()
p

```

``` {r frequency_plot_umbu-opt}

p<- ggplot(experiment_data1[!experiment_data1$VERSION == 'vanilla',], aes(SIZE,TIME, fill = VERSION)) + 
  geom_bar(stat="identity", color="black", position=position_dodge()) + 
  labs(x = "Version", y = "Time (Seconds)", title = "Umbu and Optimized Performances", fill = "Frequencies")  + theme_bw() +
  geom_errorbar(aes(ymin=TIME-sd, ymax=TIME+sd), width=.3, position=position_dodge(.9)) 
p

```

``` {r frequency_plot_umbu-opt2}

p<- ggplot(experiment_data1[!experiment_data1$VERSION == 'vanilla',], aes(VERSION,TIME, fill = SIZE)) + 
  geom_bar(stat="identity", color="black", position=position_dodge()) + 
  labs(x = "Version", y = "Time (Seconds)", title = "Umbu and Optimized Performances", fill = "Frequencies")  + theme_bw() +
  geom_errorbar(aes(ymin=TIME-sd, ymax=TIME+sd), width=.3, position=position_dodge(.9)) 
p

```

## How our Umbu solution behave as duplication rate grows?

### Performance Metric

Performance was given as the duration to run the algorithm. This duration is given by the elapsed time between the start of the program until the time it finished.

### Metodology

To this end, we executed the multi-criteria analysis on three synthetic samples. The duplication ratio in these samples is 5%, 50%, and 75%. All the samples have 176400 alternatives.

### Results

``` {r umbu_duplication_rate_plot}
experiment_data2 <- summarize(experiment_data2, varname = "TIME", groupnames = c("VERSION", "SIZE"))
experiment_data2$SIZE <- as.character(experiment_data2$SIZE)
p <- ggplot(experiment_data2, aes(VERSION, TIME, fill = SIZE)) + 
  geom_bar(stat="identity", color="black", position=position_dodge()) + 
  labs(x = "Version", y = "Time (Seconds)", title = "Umbu Performance", fill = "Frequency rate")  + theme_bw() +
  geom_errorbar(aes(ymin=TIME-sd, ymax=TIME+sd), width=.3, position=position_dodge(.9))
p

```


